Trends of SDR in Thessaloniki

### 2023-06-06 Article.Rmd
Commit 2023-06-06 12:17

The shortwave downward solar irradiance (SDR) at the Earth's surface plays s significant role, on the climate.
Changes of the SDR can be related to major changes on the factors affecting the radiative forcing balance.
Multiple studies attempt to evaluate the phenomenon and the potential causes [@Ohvril2009; @Schwarz2020; @Wild2009; @Wild2012; @Xia2007; @Zerefos2009].
Although, there are regional variation in the radiation, with both positive and negative trends, most of the studies agree that a major factor is the interaction of aerosols and clouds.

In this study we examine the trends of SDR with ground-based measurements at Thessaloniki for the period 1993 - 2023, as derived from a CM-21 pyranometer.
We reevaluate and extend the dataset used by @Bais2013, applying a different algorithm for the identification of clear-/cloud-sky instances, and we derive the radiation trends for this period under different sky conditions (all-sky, clear-sky and cloud-sky).

@@

<!-- goals -->
Here we investigate the trend on shortwave radiation for the last decades at Thessaloniki, and try to infer a relation to sky conditions (all, clear, cloudy).

@@

<!-- time span -->
The SDR is equivalent to the whole sky global radiation (GHI), and was obtained with a horizontal leveled, CM-21 pyranometer.
Data spans the period 
`r min(ALL_1_daily_DESEAS$Date)` to `r max(ALL_1_daily_DESEAS$Date)`.
In some algorithms we used as auxiliary data, the direct beam radiation (DNI) for comparisons, obtained by a CHP-1 pyrheliometer, with data availability from 
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])` to `r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.

>>>>

The shortwave downward solar irradiance (SDR) at the Earth's surface plays a significant role, on Earths climate.
Changes of the SDR can be related to major changes on factors affecting the radiative forcing balance and human activities.
Multiple studies attempt to evaluate the phenomenon and the potential causes [@Ohvril2009; @Schwarz2020; @Wild2009; @Wild2012; @Xia2007; @Zerefos2009].
Although, there is regional variation of SDR, with both positive and negative trends, most of the studies agree that the major factors are the interaction of aerosols and clouds.

In this study, we examine the trends of SDR with ground-based measurements at Thessaloniki for the period 1993 - 2023, as derived from a CM-21 pyranometer.
<!-- goals -->
We reevaluate and extend the dataset used by @Bais2013, applying a different algorithm for the identification of clear-/cloud-sky instances, and we derive the radiation trends for this period under different sky conditions (all-sky, clear-sky and cloud-sky).

@@

@@

<!-- time span -->
The SDR is equivalent to the whole sky global radiation (GHI), and was obtained with a horizontal leveled, CM-21 pyranometer.
SDR data spans the period of 
`r min(ALL_1_daily_DESEAS$Date)` to `r max(ALL_1_daily_DESEAS$Date)`.
In some algorithms we used as auxiliary data, the direct beam radiation (DNI) for comparisons, obtained by a CHP-1 pyrheliometer, with data availability from 
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])` to `r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.
